---
title: "eqvis"
author: "Kevin Baktiar"
date: "3/24/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###### A package created for Coursera, using earthquake data from the NOAA.
###### The data used is specific to the NOAA. The purpose of this package is to
###### demonstrate reading in the data, showcasing an earthquake timeline, and
###### showing an interactive map of specific earthquakes.

#### Installation

```{r echo= TRUE, results='hide'}
library(eqvis)
```
```{r include=FALSE}
library(dplyr)
library(ggplot2)
library(grid)
library(maps)
library(leaflet)
library(lubridate)
```


#### Reading In Data

```{r echo=TRUE}
file_url <- "https://www.ngdc.noaa.gov/nndc/struts/results?type_0=Exact&query_0=$ID&t=101650&s=13&d=189&dfn=signif.txt"
raw_data <- read.delim(file_url)
```

#### Cleaning Up The Data

```{r echo=TRUE}
source('~/eqvis/eq_clean_data.R')
cleaned_data_example <- eq_clean_data(raw_data)
head(cleaned_data_example)
```

#### Visualizing The Data On A Timeline

```{r echo=TRUE}
source('~/eqvis/geom_timeline.R')
ggplot(data=subset(cleaned_data_example, !is.na(EQ_PRIMARY) & COUNTRY %in% c("USA", "CHINA")),
 aes(x = DATE, y = COUNTRY, size = EQ_PRIMARY, xmin = as.Date('2000-01-01',"%Y-%m-%d"),
    xmax = as.Date('2016-12-31',"%Y-%m-%d"), color = DEATHS, fill = DEATHS, label = LOCATION_NAME)) +
  geom_timeline(alpha = .5) +
  scale_size_continuous(name = "Richter Scale Value") +
  scale_color_continuous(name = "# Deaths") +
  scale_fill_continuous(guide=FALSE) +
  labs(y = "") +
  theme(legend.position = "bottom",
        legend.key = element_blank(), legend.box = "horizontal", panel.background = element_blank(),
        axis.line.x = element_line(size = .5, color = "black"), axis.ticks.x = element_line(size = .5))
```

#### Visualizing The Data On A Interactive Map

```{r echo=TRUE}
source('~/eqvis/eq_map.R')
cleaned_data_example %>%
  dplyr::filter(COUNTRY == "MEXICO" & lubridate::year(DATE) >= 2000) %>%
  dplyr::mutate(popup_text = eq_create_label(.)) %>%
  eq_map(annot_col = "popup_text")
```

